### 2017-09-09 paper/evaluation.tex
Working on RQ7

We used the following methodology to select projects for
analysis. After obtaining the list of potential projects from GitHub, we filtered those
containing a \pomf{} file in the root directory.\Comment{  A Maven project may
contain several sub-modules with multiple \pomf{} files.}
Then, considering this set of Maven projects, we
executed the tests for \SubjectsReruns{} times to discard those projects with
issues
in the build file and non-deterministic results observed from sequential executions.
As of August 25th 2017, our search criteria returned a total of \SubjectsGithub{}
subjects.
From this set of projects,
\SubjectsGithubNotMaven{} projects were not Maven or did not have a
\pomf{} in the root directory, 
\SubjectsGithubNotTestable{} projects were not considered because of
environment incompatibility
(\eg, missing\Comment{ required web browser or database management system}~DBMS),
\SubjectsGithubFlaky{} projects were discarded because of
``flaky tests''~\cite{luo-etal-fse2014}. A ``flaky'' test is a test that passes or fails under
the same circumstances leading to non-deterministic results.
As some of our experiments consist of running tests on different
threads, we ignored these projects as it would be impractical
to identify whether a test failed due to a race condition or some
other source of flakiness.
From the remaining \SubjectsGithubConsistant{} projects with
deterministic results, we eliminated \SubjectsGithubTooManyFailures{}
projects with \SuiteFailingThreshold{} or more failing tests as to
reduce bias. For the
remaining projects with failing tests, we used the JUnit's
\CodeIn{@Ignore} annotation to ignore failing tests.
Our final set of subjects contains \numSubjs{} projects.
Figure~\ref{fig:subjects} summarizes our sample set.

@@

\begin{center}
\fbox{
\begin{minipage}{8cm}
  \textit{Answering \numRQFeasibilityTwo{}:}~\emph{Overall, results indicate that
  projects with a very small number of tests monopolizing end-to-end
  execution time were rare. Time most often is distributed evenly
  across test cases.}
\end{minipage}
}
\begin{figure}[h!]
  \centering
  \begin{subfigure}{0.13\textwidth}
    \centering
    \includegraphics[width=.9\textwidth]{results/boxplots-testcases.pdf}
    \caption{\label{fig:size-testsuites}}
  \end{subfigure}
  \hspace{3ex}
  \begin{subfigure}{0.28\textwidth}
    \centering
    \includegraphics[width=.9\textwidth]{results/scatter-testcost.pdf}
    \caption{\label{fig:scattercost}}
  \end{subfigure}
  \caption{\label{fig:time-versus-size}(a) Size of test suites; (b)
    Size versus running time of test suites.}%
\end{figure}
\end{center}

@@

To answer \numRQAdoptionOne{} we used projects from the \medg{} and
\longg{} groups where parallelization can be more helpful. We used a
dynamic and a static approach to find manifestations of
parallelism. We discuss results obtained with these complementary
approaches in the following.

@@

Considering

@@

test modules. Table~\ref{tab:freqmodes-dynamic} shows the
\numProjectsPar{} projects we identified where parallelism is enabled by default in Maven.

@@

%    \vspace{-1ex}

@@

configuration. It came as a surprise the observation that
no project used distinct configurations in their modules.

\subsubsection{Static checking}
\label{sec:rqC-2}
Given that the dynamic approach cannot detect parallelism manifested
through the default
configuration of projects, we also searched for indications of parallelism in build
files\Comment{ in the same sample set of \numMedLong{} projects}.  We
parsed all \emph{pom.xml} files under the project's directory and used
the same approach as in our previous analysis to classify
configurations.  We noticed initially that our approach was unable to
infer the configuration mode for cases where the decision depends on
the input (\eg,
\CodeIn{<parallel>\$\{parallel.type\}</parallel>}). For these
projects, the tester needs to provide additional parameters in the
command line to enable parallelization (\eg, \CodeIn{mvn test
  -Dparallel.type=classesAndMethods}). To handle those cases, we
considered all possible values for the parameter (in this case,
\CodeIn{\$\{parallel.type\}}).  It is also important to note that this
approach is not immune to false negatives, which can occur when
\emph{pom.xml} files are encapsulated in jar files or files downloaded from
the network.  Consequently, this approach complements the
the dynamic approach. Overall, we found \numProjectsParStatic{}
projects manifesting parallelism with this approach.
Compared to the set of projects listed in
Table~\ref{tab:freqmodes-dynamic}, we found four new projects, namely:
\CodeIn{Google Cloud\Comment{ Platform} DataflowJavaSDK} (using
configuration \ParClassParMeth), \CodeIn{Mapstruct} (using configuration
\ForkSeq{}), \CodeIn{T-SNE-Java} (using configuration \ForkSeq), and
\CodeIn{Urbanairship Datacube} (using configuration \ParClassParMeth).
Curiously, we also found that project \CodeIn{Jcabi}, \CodeIn{Rultor},
and \CodeIn{Takes} were not detected using this methodology.
That happened because these projects loaded a \emph{pom.xml} file from
a jar file that we missed.
Considering the static and dynamic methods together, we found a total
of \numProjectsParTotal{} distinct projects using parallelism,
corresponding to the union of the two subject sets.

@@

To answer this research question we surveyed developers involved in a
selection of projects from our benchmark with time-consuming test
suites.  The goal of the survey is to better comprehend developer's
attitude towards the use of parallelism as a mechanism to speedup
regression testing.  We surveyed developers from a total of
\emailsProjects{} projects.  From the initial list of \numMedLong{}
project, we discarded 11 projects that we knew a priori used
parallelization, and \discartedProjects{} projects that we could not find
developer's emails from commit logs.  From this list of projects, we
mined potential participants for our study.  More precisely, we
searched for developer's name and email from the last 20 commits to
the corresponding project repository.  Using this approach, we
identified a total of \emailsSent{} eligible participants.  Finally,
we sent plain-text e-mails, containing the survey, to those developers.  In
total, \emailsAnswered{} developers replied but we discarded
\emailsFalseAnswers{} replies with subjective answers.  Considering
projects covered by the answers, a total of \emailsProjectsAnswered{}
projects (\percEmailsProjectsAnswered{} of the total) were represented
in those replies. \Luis{In one specific case, one developer worked in
  multiple projects, and we consider it as a different answer.}
Note that multiple developers on each project
received emails.  We sent the following set of questions to
developers:

@@

To answer this research question, we selected ten different subjects,
ran their test suites against all configurations described in
Section~\ref{sec:modes}, and compared their running times and rate of
test flakiness.  We used the sequential execution (configuration
\emph{\Seq{}}) associated with each project as the comparison baseline
in this experiment.  We selected subjects from the medium and long
groups from Section~\ref{sec:rqA} and further selected their longest
test module for testing.  The rationale for this selection was to
obtain a diverse set of subjects exposing a wide range of running
times (range observed 1.1m-8.2m) and number of test cases (range
observed 54-17,513) and yet be able to run the experiment in
reasonable time.  We ran each project on each configuration with ten
seeds.  Overall, we needed to reran test suites 600 times, 60 times
(10x6 configurations) on each project.  Given the low standard
deviations observed in our measurements we consider ten seeds
reasonable for this experiment.
%% \Jbc{Is this
%%   legit/acceptable/convincing?  $\rightarrow$}The rationale for this
%% criteria was to maximize the diversity of domains from the subjects,
%% assuming these subjects have test suites with different
%% characteristics (\eg, architectural design and rate of cpu/io-bound
%% operations).
%% Notice that with parallelism enabled, the
%% number of failing tests may vary on different runs due to the
%% non-deterministic scheduling of threads and processes.  For that
%% reason, we re-executed the experiment and computed the average speedup
%% and flakiness on each scenario.
%%    The rationale for this selection criteria was to maximize the chances
%%    of observing speedup and flakiness, assuming that long-running tests
%%    also have many tests. Indeed, we confirmed that test suites in these
%%    projects contain at least 236 tests ($1,662.7$ in average).
%% 
%% In a first attempt of this experiment, we considered using Maven to
%% run the subjects on the different parallel configurations. However,

@@

%%  LocalWords:  RQ occurence parallelization Tradeoffs API readme th
%%  LocalWords:  mvn clearcut escapeinside xleftmargin untestable LTS
%%  LocalWords:  framexleftmargin CPUs Tahr sysstat gh Vagrantfile FC
%%  LocalWords:  javadoc isolcpus JUnit's JUnitCore Gligoric boxplots
%%  LocalWords:  outliers apache uber chaperone facebookarchive AWS
%%  LocalWords:  linkbench priori SDK GoogleCloud Moquette JVMs dir
%%  LocalWords:  xml basicstyle boxpos numberstyle deletekeywords JVM
%%  LocalWords:  uncompilable leftmargin quartile DskipTests forkMode
%%  LocalWords:  threadCount forkCount lrr BounceStorage Flink Gerrit
%%  LocalWords:  JenkinsCI Spotify Javaslang Jcabi Github Hazelcast
%%  LocalWords:  Jankotek MapDB Dparallel classesAndMethods Mapstruct
%%  LocalWords:  DataflowJavaSDK modularized JUnit llrrr lightgray rr
%%  LocalWords:  GitHub amongst Xeon runtime Scalability Dataflow sdk
%%  LocalWords:  JCTools RipMe classpath ParallelComputer livelock io
%%  LocalWords:  mapdb workflow XPath boxplot llcr javaslang jcabi
%%  LocalWords:  github hazelcast jankotek OpenNLP yegor Rultor vavr
%%  LocalWords:  Vavr SNE Urbanairship Datacube

>>>>

We used the following methodology to select projects for
analysis. After obtaining the list of potential projects from GitHub, we filtered those
containing a \pomf{} file in the root directory.\Comment{  A Maven project may
contain several sub-modules with multiple \pomf{} files.}
Then, considering this set of Maven projects, we
executed the tests for \SubjectsReruns{} times to discard those projects with
issues
in the build file and nondeterministic results observed from sequential executions.
As of August 25th 2017, our search criteria returned a total of \SubjectsGithub{}
subjects.
From this set of projects,
\SubjectsGithubNotMaven{} projects were not Maven or did not have a
\pomf{} in the root directory, 
\SubjectsGithubNotTestable{} projects were not considered because of
environment incompatibility
(\eg, missing\Comment{ required web browser or database management system}~DBMS),
\SubjectsGithubFlaky{} projects were discarded because of
``flaky tests''~\cite{luo-etal-fse2014}. A ``flaky'' test is a test that passes or fails under
the same circumstances leading to non-deterministic results.
As some of our experiments consist of running tests on different
threads, we ignored these projects as it would be impractical
to identify whether a test failed due to a race condition or some
other source of flakiness.
From the remaining \SubjectsGithubConsistant{} projects with
deterministic results, we eliminated \SubjectsGithubTooManyFailures{}
projects with \SuiteFailingThreshold{} or more failing tests as to
reduce bias. For the
remaining projects with failing tests, we used the JUnit's
\CodeIn{@Ignore} annotation to ignore failing tests.
Our final set of subjects contains \numSubjs{} projects.
Figure~\ref{fig:subjects} summarizes our sample set.

@@

\begin{center}
\fbox{
\begin{minipage}{8cm}
  \textit{Answering \numRQFeasibilityTwo{}:}~\emph{Overall, results indicate that
  projects with a very small number of tests monopolizing end-to-end
  execution time were rare. Time most often is distribuited evenly
  across test cases.}
\end{minipage}
}
\begin{figure}[h!]
  \centering
  \begin{subfigure}{0.13\textwidth}
    \centering
    \includegraphics[width=.9\textwidth]{results/boxplots-testcases.pdf}
    \caption{\label{fig:size-testsuites}}
  \end{subfigure}
  \hspace{3ex}
  \begin{subfigure}{0.28\textwidth}
    \centering
    \includegraphics[width=.9\textwidth]{results/scatter-testcost.pdf}
    \caption{\label{fig:scattercost}}
  \end{subfigure}
  \caption{\label{fig:time-versus-size}(a) Size of test suites; (b)
    Size versus running time of test suites.}%
\end{figure}
\end{center}

@@

To answer \numRQAdoptionOne{}, we selected all projects from the \medg{} and
\longg{} groups, \ie, projects that ran in at least one minute.  This
set includes \numMedLong{} projects (see Section~\ref{sec:rqA}).  We
looked for dynamic and static manifestations of parallelism.

%% The
%% following section report results for each of these cases.

@@

It came as a surprise the observation that
no project used distinct configurations in their modules. Considering

@@

test modules.
Table~\ref{tab:freqmodes-dynamic} shows the \numProjectsPar{} projects
we identified where parallelism is enabled by default in Maven.
configuration.

@@

    \vspace{-1ex}

@@

\subsubsection{Static checking}
\label{sec:rqC-2}
As our previous approach cannot detect parallelism in non-default
configurations, we also looked for indication of parallelism in build
files\Comment{ in the same sample set of \numMedLong{} projects}.  We
parsed all \emph{pom.xml} files under the project's directory and used
the same approach as in our previous analysis to classify
configurations.  We noticed initially that our approach was unable to
infer the configuration mode for cases where the decision depends on
the input (\eg,
\CodeIn{<parallel>\$\{parallel.type\}</parallel>}). For these
projects, the tester needs to provide additional parameters in the
command line to enable parallelization (\eg, \CodeIn{mvn test
  -Dparallel.type=classesAndMethods}). To handle those cases, we
considered all possible values for the parameter (in this case,
\CodeIn{\$\{parallel.type\}}).  It is also important to note that this
approach is not immune to false negatives, which can occur when
\emph{pom.xml} files are encapsulated in jar files or files downloaded from
the network.  Consequently, this static checking is complementary to
the dynamic checking, previously presented.

This methodology founds \numProjectsParStatic{} projects.
Compared to the set of projects listed in
Table~\ref{tab:freqmodes-dynamic}, we found four new projects, namely:
\CodeIn{Google Cloud\Comment{ Platform} DataflowJavaSDK} (using
configuration \ParClassParMeth), \CodeIn{Mapstruct} (using configuration
\ForkSeq{}), \CodeIn{T-SNE-Java} (using configuration \ForkSeq), and
\CodeIn{Urbanairship Datacube} (using configuration \ParClassParMeth).
Curiously, we also found that project \CodeIn{Jcabi}, \CodeIn{Rultor},
and \CodeIn{Takes} were not detected using this methodology.
That happened because these projects loaded a \emph{pom.xml} file from
a jar file that we did not check.
Considering the static and dynamic methods together, we found a total
of \numProjectsParTotal{} distinct projects using parallelism,
corresponding to the union of the two subject sets.

@@

To answer this research question we surveyed developers involved in a
selection of projects from our benchmark with time-consuming test
suites.  The goal of the survey is to better comprehend developer's
attitude towards the use of parallelism as a mechanism to speedup
regression testing.  We surveyed developers from a total of
\emailsProjects{} projects.  From the initial list of \numMedLong{}
project, we discarded 11 projects that we knew a priori used
parallelization, and \discartedProjects{} projects that we could not find
developer's emails from commit logs.  From this list of projects, we
mined potential participants for our study.  More precisely, we
searched for developer's name and email from the last 20 commits to
the corresponding project repository.  Using this approach, we
identified a total of \emailsSent{} eligible participants.  Finally,
we sent plain-text e-mails, containing the survey, to those developers.  In
total, \emailsAnswered{} developers replied but we discarded
\emailsFalseAnswers{} replies with subjective answers.  Considering
projects covered by the answers, a total of \emailsProjectsAnswered{}
projects (\percEmailsProjectsAnswered{} of the total) were represented
in those replies.  Note that multiple developers on each project
received emails.  We sent the following set of questions to
developers:

@@

To answer this research question, we selected 20 different subjects,
ran their test suites against all configurations described in
Section~\ref{sec:modes}, and compared their running times and rate of
test flakiness.
We used the sequential execution associated with each project as the
comparison baseline in this experiment.
We sorted the subjects by decreasing order of execution time and
selected the first 20 projects that uses JUnit 4.7 or later.
The rationale for this criteria was to ensure compatibility with
parallel configuration since older versions of JUnit does not support
parallel testing.
We ran each project on each configuration for 10 times with with ten seeds.
Overall, we needed to reran test suites 600 times, 60 times (10x6
configurations) on each project.
Given the low standard deviations observed in our measurements we
consider ten seeds reasonable for this experiment.
%% \Jbc{Is this
%%   legit/acceptable/convincing?  $\rightarrow$}The rationale for this
%% criteria was to maximize the diversity of domains from the subjects,
%% assuming these subjects have test suites with different
%% characteristics (\eg, architectural design and rate of cpu/io-bound
%% operations).
%% Notice that with parallelism enabled, the
%% number of failing tests may vary on different runs due to the
%% non-deterministic scheduling of threads and processes.  For that
%% reason, we re-executed the experiment and computed the average speedup
%% and flakiness on each scenario.
%%    The rationale for this selection criteria was to maximize the chances
%%    of observing speedup and flakiness, assuming that long-running tests
%%    also have many tests. Indeed, we confirmed that test suites in these
%%    projects contain at least 236 tests ($1,662.7$ in average).
%% 
%% In a first attempt of this experiment, we considered using Maven to
%% run the subjects on the different parallel configurations. However,

@@

%%  LocalWords:  RQ occurence parallelization Tradeoffs API readme th
%%  LocalWords:  mvn clearcut escapeinside xleftmargin untestable LTS
%%  LocalWords:  framexleftmargin CPUs Tahr sysstat gh Vagrantfile FC
%%  LocalWords:  javadoc isolcpus JUnit's JUnitCore Gligoric boxplots
%%  LocalWords:  outliers apache uber chaperone facebookarchive AWS
%%  LocalWords:  linkbench priori SDK GoogleCloud Moquette JVMs dir
%%  LocalWords:  xml basicstyle boxpos numberstyle deletekeywords JVM
%%  LocalWords:  uncompilable leftmargin quartile DskipTests forkMode
%%  LocalWords:  threadCount forkCount lrr BounceStorage Flink Gerrit
%%  LocalWords:  JenkinsCI Spotify Javaslang Jcabi Github Hazelcast
%%  LocalWords:  Jankotek MapDB Dparallel classesAndMethods Mapstruct
%%  LocalWords:  DataflowJavaSDK modularized JUnit llrrr lightgray rr
%%  LocalWords:  GitHub amongst Xeon runtime Scalability Dataflow sdk
%%  LocalWords:  JCTools RipMe classpath ParallelComputer livelock
%%  LocalWords:  mapdb workflow XPath
